\section{Related Work}
\label{sec:related}


% White Space
Since white space bands became available for wireless communication, many efforts have been 
put forward in the area for the application of white space bands.~\cite{fccwhitespace} 
In~\cite{bahl2009white}, the author considered a cognitive method to avoid collision 
between white space communication and TV broadcasting. 
Many works that increase the convenience of using white space databases have been published 
(e.g., Microsoft's White Space Database~\cite{msdatabase}).
Google has even visualized the licensed white space channels 
in US cities with an API for both research and commercial use~\cite{googledatabase}.
Previous work has studied point to point communication with white space bands~\cite{cui2013leveraging}, 
and wireless network deployment with many white space channels~\cite{pcuiwinmee}.
However, many of the major cities in the US do not have many white space channels, such as Austin, TX, which has only one white space channel. 
As far as we know, there has been no work done discussing limited white space channel availability.

% Multiuser diversity
Multiuser diversity was recognized in late 1990s~\cite{heath2001multiuser}. The channel quality 
varies across users due to differences in location, environment, etc. The wireless signal transmitted through the 
air is influenced by large scale propagation, multi-path fading, and several other factors~\cite{gan2014multiple}.
Previous work has identified multiuser diversity for MIMO and beamforming applications~\cite{gao2013multiuser}.
However, few people have recognized the importance of measurements in multiuser diversity 
quantification and application.

%  Multi-channel
Applying white space to wireless networks is similar to the previous multi-channel works besides 
propagation variation. In~\cite{bodas2012low} a multi-channel system is formulated as a queuing 
system and a Server Side Greedy algorithm is proposed to optimize the throughput with low complexity. 
In~\cite{ji2013performance}, a Delay-based Queue-Side-Greedy algorithm is proposed with low complexity 
for optimal throughput and near-optimal delay.~\cite{liu2014energy} developed a multi-objective optimization 
framework to minimize energy consumption in a multi-channel multi-radio system. 
However, these works do not address minimizing the resource to achieve a certain quality of service and they assume an 
on-off channel model.

% Need to modify
The multiuser setting with a single channel has been studied previously~\cite{tan2010distributed}. 
Spectral diversity is isolated for a single user in~\cite{shu2009throughput}. In~\cite{liu2013stay}, 
multi-user dynamic channel access is proposed jointly consider the temporal and spectral diversity in a multichannel model. However, 
none of these works address the channel association problem in a multi-band scenario.
White space application in access network deployment with spectral diversity has also been studied~\cite{pcuiwinmee}. However, these works 
fail to leverage white space frequencies for multi-user diversity in both spectral and temporal scenarios.

%% Multithread
% On-off channel
Previous works in real-time systems focused on minimizing required hardware resources~\cite{nelissen2012techniques}.
In~\cite{li2014analysis}, the author proves the capacity augmentation bounds for schedulers of parallel tasks. 
However, these works assume the parallel tasks have uniform servers. 
~\cite{chen2011feasibility} investigated white space use in a queuing system without considering a 
heterogeneous topology.
In contrast, we study the performance of a heterogeneous network with both white space channels 
and WiFi channels for channel utilization. 



